LAGOS lake depth

### 2020-02-20 README.Rmd
formatting

dt <- read.csv("data/00_bathy_depth/00_bathy_depth.csv", stringsAsFactors = FALSE)
knitr::kable(setNames(data.frame(names(dt)), "field"))
```

Data: [bathymetry derived lake geometry](data/00_bathy_depth/bathy_geometry.csv)

>>>>

dt <- read.csv("data/00_bathy_depth/00_bathy_depth.csv", stringsAsFactors = FALSE)
knitr::kable(setNames(data.frame(names(dt)), "field"))
```
Data: [bathymetry derived lake geometry](data/00_bathy_depth/bathy_geometry.csv)
